---
title: "Dembo Ceesay's Website"
---
Hi, I am a first year graduate student studying AI and Business Statistics. 

While pursuing my degree in Business Administration, I was introduced to data analysis and its applications and decided to pursue it for my graduate studies. I have worked on the side as a pharmacy technician for the past 4 years while also taking on internships. 

It is due to these experiences that I chose to aim for a career in pharmaceutical data analysis. I will use my time at Baruch accumulating the skills and knowledge of the industry to ensure a quick entry into the workforce.
In my personal time I like creating digital art, gaming, and watching movies


```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```